%! Author = huibmeulenbelt
%! Date = 21/01/2026

% Preamble
\documentclass[11pt]{article}

% Packages
\usepackage{amsmath}

% Document
\begin{document}
    \title{Business case Revolut}
    \author{HJA Meulenbelt}
    \date{21-01-2026}
    \maketitle

    \section*{Introduction}
    \textbf{mmarkov} provides transparent, data-driven insights into mixed-martial arts (MMA) performances and outcomes using advanced probabilistic and statistical modeling.
    With the help of Bayesian inference and extremely granular data, \textbf{mmarkov} estimates different type of skills for each fighter.
    These estimated fighter skills helps us to derive transition probabilities in a Markov chain framework.
    Basically, a fight is represented as a Markov chain with states representing different fight situations (e.g., standing, clinch, ground) and transitions representing possible actions (e.g., strikes, takedowns, submissions).
    The properties of this Markov chain are then used to obtain insights in the fight-dynamics.

    \section*{Mission}
    The mission of \textbf{mmarkov} is to empower MMA-stakeholders with rigorous, data-backed analysis to enhance the quality of the sport.
    Examples of our target customers include:
    \begin{itemize}
        \item Sports analysts and coaches who are looking for data-driven insights into fighter performances
        \item Media outlets who seek to enhance their MMA coverage with advanced statistical analysis
        \item MMA enthusiasts interested in deeper understanding of fight dynamics and fighter skills
        \item Podcasters and commentators seeking data-backed insights for storytelling and analysis.
        \item Fantasy league players looking for an edge in drafting fighters based on skill estimates
        \item Academics who use real-world sports data to study probability and stochastic processes
    \end{itemize}


    \section*{Revenue model}
    \textbf{mmarkov} generates revenue through the following channels:
    \begin{itemize}
        \item Subscription access to premium analytics dashboards
        \item Custom reports and deep-dive analyses for media outlets, analysts and coaches
        \item Licensing of proprietary models and datasets to interested third parties
        \item Educational content and tools
    \end{itemize}

    Important to note: no financial or wagering recommendations are provided by \textbf{mmarkov}.

    \section*{Landscape analysis}
    The main peer of \textbf{mmarkov} is \textbf{DataGolf} in the golf domain.They provide advanced analytics and statistics for golf enthusiasts, media, and professionals.
    Their platform (\textit{www.datagolf.com}) uses advanced stats and models to analyze player performance and course difficulty.

    Summarized, \textbf{mmarkov} fills a unique niche in the MMA analytics space by combining advanced probabilistic modeling with granular fight data to provide actionable insights for a variety of stakeholders.

\end{document}